---
title: "SwedishElectionData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SwedishElectionData-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## API and Package

This package extracts data from the web API provided by Valmyndigheten to access the Swedish election results from 2014. 


## Data
The output is a data frame with either level: landsting, riksdag, or kommun and type of either: kommun or valdistrikt. It shows the top 5 municipalities with the total number of votes for each party.  

## How to Use  

To install package:  

``` r
install.packages("zoepatton/SwedishElectionData")
```  

To use function:
``` r
election_data(level="landsting",type="kommun")
```   


To install and run the corresponding shiny app:  

``` r
library(shiny)
library(SwedishElectionData)
runGitHub("SwedishElectionData-Shiny","zoepatton")
```  



```{r setup}
library(SwedishElectionData)
```
